\documentclass[12pt]{article}
\usepackage{acl2005}
\usepackage{times}
\usepackage{latexsym}

\begin{document}


\begin{thebibliography}{}


\vspace{2mm}
\bibitem[\protect\citename{Mani}2005]{Mani:05}
Mani, Inderjeet.
\newblock 2005.
\newblock {\em Time Expression Tagger and Normalizer.}
\newblock http://complingone.georgetown.edu/~linguist/GU\_TIME\_DOWNLOAD.HTML

\bibitem[\protect\citename{ManiShiffman}forthcoming]{Mani:forth}
Mani, Inderjeet and Barry Schiffman.
\newblock Forthcoming.
\newblock 'Temporally Anchoring and Ordering Events in News'.
\newblock  James Pustejovsky and Robert Gaizauskas (eds.)
\newblock {\em Event Recognition in Natural Language}.
\newblock John Benjamins.

\bibitem[\protect\citename{Pustejovsky and others}2003a]{Pustejovsky:03a}
Pustejovsky, J., J. Casta\~{n}o, R. Ingria, R. Saur\'{\i}, R. Gaizauskas, A. Setzer, and G. Katz.
\newblock 2003a.
\newblock TimeML: Robust Specification of Event and Temporal Expressions in Text.
\newblock {\em IWCS-5 Fifth International Workshop on Computational Semantics.}

\bibitem[\protect\citename{Pustejovsky and others}2003b]{Pustejovsky:03b}
Pustejovsky J., P. Hanks, R. Saur\'{\i}, A. See, R. Gaizauskas, A. Setzer, D. Radev, B. Sundheim, D. Day, L. Ferro and M. Lazo.
\newblock 2003b.
\newblock The TIMEBANK Corpus.
\newblock {\em Proceedings of Corpus Linguistics 2003}:
\newblock 647-656.

\bibitem[\protect\citename{Pustejovsky and others}2004]{Pustejovsky:04}
Pustejovsky, J.,  R. Saur\'{\i}, J. Casta\~{n}o, D. R. Radev, R. Gaizauskas, A. Setzer, B. Sundheim and G. Katz.
\newblock 2004.
\newblock Representing Temporal and Event Knowledge for QA Systems.
\newblock Mark T. Maybury (ed.)
\newblock {\em New Directions in Question Answering}.
\newblock MIT Press, Cambridge.

\bibitem[\protect\citename{Pustejovsky and others}2005]{Pustejovsky:2005}
Pustejovsky, James, Martha Palmer and Adam Meyers.
\newblock 2005.
\newblock
\newblock Workshop on Frontiers in Corpus Annotation II. Pie in the Sky. ACL 2005.

\bibitem[\protect\citename{Pustejovsky and others}forth]{Pustejovsky:forth}
Pustejovsky, J., B. Knippen, J. Littman, R. Saur\'{\i}
\newblock (forthcoming)
\newblock Temporal and Event Information in Natural language Text.
\newblock {\em Language Resources and Evaluation}.

\bibitem[\protect\citename{Sauri and others}2004]{Sauri:04}
Saur\'{\i}, Roser, Jessica Littman, Robert Knippen, Rob Gaizauskas, Andrea Setzer and James Pustejovsky.
\newblock 2004.
\newblock {\em TimeML Annotation Guidelines}.
\newblock http://www.timeml.org.

\bibitem[\protect\citename{Sauri and Verhagen}2005]{Sauri:05}
Saur\'{\i}, Roser and Marc Verhagen.
\newblock 2005.
\newblock Temporal Information in Intensional Contexts.
\newblock Bunt, H., J. Geertzen and E. Thijse (eds.)
\newblock {\em Proceedings of the Sixth International Workshop on Computational Semantics}.
\newblock Tilburg, Tilburg University:
\newblock 404-406.

\bibitem[\protect\citename{Verhagen and Knippen}forth]{VerhagenKinppen:forth}
Verhagen, Marc and Robert Knippen.
\newblock Forthcoming.
\newblock TANGO: A Graphical Annotation Environment for Ordering Relations.
\newblock James Pustejovsky and Robert Gaizauskas (eds.)
\newblock {\em Time and Event Recognition in Natural Language}.
\newblock John Benjamin Publications.

\bibitem[\protect\citename{Verhagen and others}2005]{VerhagenOthers:2005}
Verhagen, Marc, Inderjeet Mani, Roser Saur\'{\i}, Robert Knippen, Jess Littman and James Pustejovsky.
\newblock 2005.
\newblock 'Automating Temporal Annotation with TARSQI'.
\newblock Demo Session.
\newblock {\em Proceedings of the ACL 2005}.



\end{thebibliography}

\end{document}

